Data Management for LSST Special Programs

### 2023-10-19 sec_sci.tex
improve req links

\textbf{Special Processing should be done by Rubin Data Management to 
produce unique and separate data products
for Special Programs when it is both possible and necessary.}

@@

The definitions of possible and necessary, and the scope of Special Processing,
are ultimately left to the discretion of Rubin Data Management in Operations.
Note that secondary science goals may be considered as ``not necessary".

@@

\item To meet the requirement that Rubin Observatory produce
unique, separate, and joinable data products whenever this is possible 
with the original or reconfigured versions of the LSST Science Pipelines
(Section~\ref{sec:req}).

@@

@@

Rubin Observatory will reserve 10\% of its total data processing capacity for users.
This is already a requirement, as mentioned in Section~\ref{ssec:req_ug}.
This component would include {\it all} user processing and re-processing of any and 
all LSST data, including Special Programs.

>>>>

\textbf{Special Processing should be done by Rubin Data Management to 
produce unique and separate (and joinable) data products
for Special Programs when it is both possible and necessary.}

@@

@@

\item To meet the requirement that Rubin Observatory produce
unique, separate, and joinable data products whenever this is possible 
with the original or reconfigured versions of the LSST Science Pipelines
(Section~\ref{ssec:req_dp}).

@@

The definitions of possible and necessary are further illustrated with examples in Section~\ref{ssec:proc_special}.
Note that secondary science goals may be considered as ``not necessary".

The general scope of Special Processing, including situations in which cross-match and table joins 
would be possible and scientifically relevant, 
are ultimately left to the discretion of Rubin Data Management in Operations.

@@

Rubin Observatory will reserve 10\% of its total data processing capacity for users.
This component would include {\it all} user processing and re-processing of any and 
all LSST data, including Special Programs. 
This is already a requirement, as mentioned in Section~\ref{ssec:req_proc}.
